\cvitem{[248]}{\textbf{O'Donnell, Daniel Paul}. 2026c. "How to draw syntactic trees." February 1. https://people.uleth.ca/~daniel.odonnell/blog/how-to-draw-syntactic-trees.}
\cvitem{[247]}{\textbf{O'Donnell, Daniel Paul}. 2026b. "Blast from the past: McEwan, Ian. The Innocent. Knopf Canada, 2014." January 31. https://people.uleth.ca/~daniel.odonnell/blog/blast-from-the-past-mcewan-ian-the-innocent-knopf-canada-2014.}
\cvitem{[246]}{\textbf{O'Donnell, Daniel Paul}. 2026a. "And then you die. Barker, Pat. 1999. Another World. Penguin Books Ltd." January 10. https://people.uleth.ca/~daniel.odonnell/blog/and-then-you-die-barker-pat-1999-another-world-penguin-books-ltd.}
\cvitem{[245]}{\textbf{O'Donnell, Daniel Paul}. 2025g. "Cadet Branch. Brandreth. 2025. Somewhere, a Boy and a Bear: A. A. Milne and the Creation of Winnie-the-Pooh." December 28. https://people.uleth.ca/~daniel.odonnell/blog/cadet-branch-brandreth-2025-somewhere-a-boy-and-a-bear-a-a-milne-and-the-creation-of-winnie-the-pooh.}
\cvitem{[244]}{\textbf{O'Donnell, Daniel Paul}. 2025f. "The fainting couch: Norah Vincent, Self-made man (Viking 2006)." December 24. https://people.uleth.ca/~daniel.odonnell/blog/the-fainting-couch-norah-vincent-self-made-man-viking-2006.}
\cvitem{[243]}{\textbf{O'Donnell, Daniel Paul}. 2025e. "The doctor without patients: Brian Deer, The Doctor who Fooled the World." November 29. https://people.uleth.ca/~daniel.odonnell/blog/the-doctor-without-patients-brian-deer-the-doctor-who-fooled-the-world.}
\cvitem{[242]}{\textbf{O'Donnell, Daniel Paul}. 2025d. "Using a split keyboard and the recording function on the Roland FP30x." August 21. https://people.uleth.ca/~daniel.odonnell/blog/using-a-split-keyboard-and-the-recording-function-on-the-roland-fp30x.}
\cvitem{[241]}{\textbf{O'Donnell, Daniel Paul}. 2025c. "Using AI and "monitor reports" to create a departmental class schedule for outlook." August 21. https://people.uleth.ca/~daniel.odonnell/blog/using-ai-and-monitor-reports-to-create-a-departmental-class-schedule-for-outlook.}
\cvitem{[240]}{\textbf{O'Donnell, Daniel Paul}. 2025b. "Fixed: Recording is not working on new Roland FP-30x (answer: factory reset)." August 8. https://people.uleth.ca/~daniel.odonnell/blog/fixed-recording-is-not-working-on-new-roland-fp-30x-answer-factory-reset.}
\cvitem{[239]}{\textbf{O'Donnell, Daniel Paul}. 2025a. "Another Another Week!." July 21. https://people.uleth.ca/~daniel.odonnell/blog/another-another-week.}
\cvitem{[238]}{\textbf{O'Donnell, Daniel Paul}. 2024t. "Console in Obsidian Android." December 28. https://people.uleth.ca/~daniel.odonnell/blog/console-in-obsidian-android.}
\cvitem{[237]}{\textbf{O'Donnell, Daniel Paul}. 2024s. "Working on code with ChatGPT: Some tips (some also useful more generally)." December 24. https://people.uleth.ca/~daniel.odonnell/blog/working-on-code-with-chatgpt-some-tips-some-also-useful-more-generally.}
\cvitem{[236]}{\textbf{O'Donnell, Daniel Paul}. 2024r. "Witness statement to the Standing Committee on Science and Research (SRSR), November 28, 2024." November 30. https://people.uleth.ca/~daniel.odonnell/blog/witness-statement-to-the-standing-committee-on-science-and-research-srsr-november-28-2024.}
\cvitem{[235]}{\textbf{O'Donnell, Daniel Paul}. 2024q. "Party like it's 1999: Appel, Kennyism (Dundurn Press, 2024) and Ganz, When the Clock Broke (FSG, 2024)." June 30. https://people.uleth.ca/~daniel.odonnell/blog/party-like-it-s-1999-appel-kennyism-dundurn-press-2024-and-ganz-when-the-clock-broke-fsg-2024.}
\cvitem{[234]}{\textbf{O'Donnell, Daniel Paul}. 2024p. ""Tell me I've led a good life; tell me I'm a good man": WWII and the Greatest Generation at home (Band of Brothers, In a Lonely Place, Let there be light)." April 8. https://people.uleth.ca/~daniel.odonnell/blog/tell-me-i-ve-led-a-good-life-tell-me-i-m-a-good-man-wwii-and-the-greatest-generation-at-home-band-of-brothers-in-a-lonely-place-let-there-be-light.}
\cvitem{[233]}{\textbf{O'Donnell, Daniel Paul}. 2024o. "Calm, Slippery, and sadistic: My Silent War by Kim Philby and A Spy among Friends by Ben MacIntyre." March 24. https://people.uleth.ca/~daniel.odonnell/blog/calm-slippery-and-sadistic-my-silent-war-by-kim-philby-and-a-spy-among-friends-by-ben-macintyre.}
\cvitem{[232]}{\textbf{O'Donnell, Daniel Paul}. 2024n. "ChatBot prompt thyself." March 5. https://people.uleth.ca/~daniel.odonnell/blog/chatbot-prompt-thyself.}
\cvitem{[231]}{\textbf{O'Donnell, Daniel Paul}. 2024m. "What a fuss about an omelette! Why lies are protected speech in the U.S. (Liar in a crowded theater; Kosseff 2023)." March 1. https://people.uleth.ca/~daniel.odonnell/blog/what-a-fuss-about-an-omlette-why-lies-are-protected-speech-in-the-us.}
\cvitem{[230]}{\textbf{O'Donnell, Daniel Paul}. 2024l. "Blow by blow: Island Victory, S.L.A. Marshall 1944/2002." March 1. https://people.uleth.ca/~daniel.odonnell/blog/blow-by-blow-island-victory-sla-marshall-1944-2002.}
\cvitem{[229]}{\textbf{O'Donnell, Daniel Paul}. 2024k. "Seen the movie: Greene, Ministry of Fear (1943)." February 24. https://people.uleth.ca/~daniel.odonnell/blog/seen-the-movie-greene-ministry-of-fear-1943.}
\cvitem{[228]}{\textbf{O'Donnell, Daniel Paul}. 2024j. "The Eternal Present of the Spot in time: An episodic history of American higher education (Mattingly 2017, American academic cultures)." February 20. https://people.uleth.ca/~daniel.odonnell/blog/the-eternal-present-of-the-spot-in-time-an-episodic-history-of-american-higher-education-mattingly-2017-american-academic-cultures.}
\cvitem{[227]}{\textbf{O'Donnell, Daniel Paul}. 2024i. "Pervatory, by R.M. Vaughan (2023)." February 17. https://people.uleth.ca/~daniel.odonnell/blog/pervatory-by-rm-vaughan-2023.}
\cvitem{[226]}{\textbf{O'Donnell, Daniel Paul}. 2024h. "A brave attempt to address extremism: Alberta, 2023. The Kingdom, the Power, and the Glory: American Evangelicals in an Age of Extremism." February 13. https://people.uleth.ca/~daniel.odonnell/blog/a-brave-attempt-to-address-extremism-alberta-2023-the-kingdom-the-power-and-the-glory-american-evangelicals-in-an-age-of-extremism.}
\cvitem{[225]}{\textbf{O'Donnell, Daniel Paul}. 2024g. "Bockoven, 2018. Fantasticland." February 4. https://people.uleth.ca/~daniel.odonnell/blog/bockoven-2018-fantasticland.}
\cvitem{[224]}{\textbf{O'Donnell, Daniel Paul}. 2024f. "Turner, 2015. Philology the forgotten origins of the modern humanities." January 26. https://people.uleth.ca/~daniel.odonnell/blog/turner-2015-philology-the-forgotten-origins-of-the-modern-humanities.}
\cvitem{[223]}{\textbf{O'Donnell, Daniel Paul}. 2024e. "Prose, Nita. 2022. The Maid." January 12. https://people.uleth.ca/~daniel.odonnell/blog/prose-nita-2022-the-maid.}
\cvitem{[222]}{\textbf{O'Donnell, Daniel Paul}. 2024d. "Marshall, 1947 [2000]. Men against Fire." January 6. https://people.uleth.ca/~daniel.odonnell/blog/marshall-1947-2000-men-against-fire.}
\cvitem{[221]}{\textbf{O'Donnell, Daniel Paul}. 2024c. "Bell 2023. Cracking the Nazi Code: The Untold Story of Canada’s Greatest Spy." January 4. https://people.uleth.ca/~daniel.odonnell/blog/bell-2023-cracking-the-nazi-code-the-untold-story-of-canadas-greatest-spy.}
\cvitem{[220]}{\textbf{O'Donnell, Daniel Paul}. 2024b. "Iceberg Slim 1969 [2011]. Pimp." January 3. https://people.uleth.ca/~daniel.odonnell/blog/iceberg-slim-1969-2011-pimp.}
\cvitem{[219]}{\textbf{O'Donnell, Daniel Paul}. 2024a. "If only... creating suspense out of nothing in Jason Bell, Cracking the Nazi Code." January 2. https://people.uleth.ca/~daniel.odonnell/blog/if-only-creating-suspense-out-of-nothing-in-jason-bell-cracking-the-nazi-code.}
\cvitem{[218]}{\textbf{O'Donnell, Daniel Paul}. 2023o. "Reichman 2019. The Future of Academic Freedom." December 31. https://people.uleth.ca/~daniel.odonnell/blog/reichman-2019-the-future-of-academic-freedom.}
\cvitem{[217]}{\textbf{O'Donnell, Daniel Paul}. 2023n. "Everett, 2001. Erasure." December 30. https://people.uleth.ca/~daniel.odonnell/blog/everett-2001-erasure.}
\cvitem{[216]}{\textbf{O'Donnell, Daniel Paul}. 2023m. "Horn 1999. Academic Freedom in Canada." December 28. https://people.uleth.ca/~daniel.odonnell/blog/horn-1999-academic-freedom-in-canada.}
\cvitem{[215]}{\textbf{O'Donnell, Daniel Paul}. 2023l. "Finkin and Post 2009. For the Common Good." December 28. https://people.uleth.ca/~daniel.odonnell/blog/finkin-and-post-2009-for-the-common-good.}
\cvitem{[214]}{\textbf{O'Donnell, Daniel Paul}. 2023k. "Dutt-Ballerstadt and Bhattacharya, eds. 2021. Civility, Free Speech, and Academic Freedom in Higher Education." December 28. https://people.uleth.ca/~daniel.odonnell/blog/dutt-ballerstadt-and-bhattacharya-eds-2021-civility-free-speech-and-academic-freedom-in-higher-education.}
\cvitem{[213]}{\textbf{O'Donnell, Daniel Paul}. 2023j. "Buckley 1951. God and Man at Yale: The Superstitions of “Academic Freedom”." December 28. https://people.uleth.ca/~daniel.odonnell/blog/buckley-1951-god-and-man-at-yale-the-superstitions-of-academic-freedom.}
\cvitem{[212]}{\textbf{O'Donnell, Daniel Paul}. 2023i. "Bérubé and Ruth, It's not Free Speech." December 26. https://people.uleth.ca/~daniel.odonnell/blog/berube-and-ruth-it-s-not-free-speech.}
\cvitem{[211]}{\textbf{O'Donnell, Daniel Paul}. 2023h. "Sinykin 2023. Big Fiction: How conglomeration changed the publishing industry and American literature." December 22. https://people.uleth.ca/~daniel.odonnell/blog/sinykin-2023-big-fiction-how-conglomeration-changed-the-publishing-industry-and-american-literature.}
\cvitem{[210]}{\textbf{O'Donnell, Daniel Paul}. 2023g. "Irony all the way down, or, why English departments can't have pub nights." December 16. https://people.uleth.ca/~daniel.odonnell/blog/irony-all-the-way-down-or-why-english-departments-can-t-have-pub-nights.}
\cvitem{[209]}{\textbf{O'Donnell, Daniel Paul}. 2023f. "Quis custodiet ipsos custodes? Review of Cheryl Foy. An introduction to university governance. Irwin Law, 2021. (Director's cut)." December 7. https://people.uleth.ca/~daniel.odonnell/blog/quis-custodiet-ipsos-custodes-review-of-cheryl-foy-an-introduction-to-university-governance-irwin-law-2021-director-s-cut.}
\cvitem{[208]}{\textbf{O'Donnell, Daniel Paul}. 2023e. "It's not about the speaker, it's about the environment: Some sketchy initial thoughts on a new/old way of understanding Academic Freedom." December 7. https://people.uleth.ca/~daniel.odonnell/blog/it-s-not-about-the-speaker-it-s-about-the-environment-some-sketchy-initial-thoughts-on-a-new-old-way-of-understanding-academic-freedom.}
\cvitem{[207]}{\textbf{O'Donnell, Daniel Paul}. 2023d. "Hot off the presses: How students use ChatGPT to prepare and write their essays. 1/n." October 17. https://people.uleth.ca/~daniel.odonnell/blog/hot-off-the-presses-how-students-use-chatgpt-to-prepare-and-write-their-essays-1-n.}
\cvitem{[206]}{\textbf{O'Donnell, Daniel Paul}. 2023c. "Literary Criticism, Colour Commentary, House of Leaves." April 2. https://people.uleth.ca/~daniel.odonnell/blog/literary-criticism-colour-commentary-house-of-leaves-and-okham-s-razor.}
\cvitem{[205]}{\textbf{O'Donnell, Daniel Paul}. 2023b. "Thinking about Chat GPT as a search tool." March 27. https://people.uleth.ca/~daniel.odonnell/blog/thinking-about-chat-gpt-as-a-search-tool.}
\cvitem{[204]}{\textbf{O'Donnell, Daniel Paul}. 2023a. "The rise of the house of Usher: Standardisation and the decline of the value proposition in post-secondary education." January 21. https://people.uleth.ca/~daniel.odonnell/blog/the-rise-of-the-house-of-usher-standardisation-and-the-decline-of-the-value-proposition-in-post-secondary-education.}
\cvitem{[203]}{\textbf{O'Donnell, Daniel Paul}. 2022h. "Yet another blog about Twitter... It reminds me of the list-serves in the 1990s." November 19. https://people.uleth.ca/~daniel.odonnell/blog/yet-another-blog-about-twitter-it-reminds-me-of-the-list-serves-in-the-1990s.}
\cvitem{[202]}{\textbf{O'Donnell, Daniel Paul}. 2022g. "Changing in binding methods... technological improvement or technique?." November 12. https://people.uleth.ca/~daniel.odonnell/blog/changing-in-binding-methods-technological-improvement-or-technique.}
\cvitem{[201]}{\textbf{O'Donnell, Daniel Paul}. 2022f. "Writing, easy and hard." October 30. https://people.uleth.ca/~daniel.odonnell/blog/writing-easy-and-hard.}
\cvitem{[200]}{\textbf{O'Donnell, Daniel Paul}. 2022e. "How to blog." October 23. https://people.uleth.ca/~daniel.odonnell/blog/what-should-one-blog-about.}
\cvitem{[199]}{\textbf{O'Donnell, Daniel Paul}. 2022d. "Fixing a persistent mic issue in Zoom on Ubuntu." October 17. https://people.uleth.ca/~daniel.odonnell/blog/fixing-a-persistent-mic-issue-in-zoom-on-ubuntu.}
\cvitem{[198]}{\textbf{O'Donnell, Daniel Paul}. 2022c. "Using Github Pages as a Webserver." October 16. https://people.uleth.ca/~daniel.odonnell/blog/using-github-pages-as-a-webserver.}
\cvitem{[197]}{\textbf{O'Donnell, Daniel Paul}. 2022b. "Time management." September 29. https://people.uleth.ca/~daniel.odonnell/blog/time-management.}
\cvitem{[196]}{\textbf{O'Donnell, Daniel Paul}. 2022a. "Quick notes on "mediumish" Jekyll theme." May 2. https://people.uleth.ca/~daniel.odonnell/blog/quick-notes-on-mediumish-jekyll-theme.}
\cvitem{[195]}{\textbf{O'Donnell, Daniel Paul}. 2021e. "Best register-change I've seen in an academic book in a while: Hayot, Humanist reason." September 20. https://people.uleth.ca/~daniel.odonnell/blog/best-register-change-i-ve-seen-in-an-academic-book-in-a-while-hayot-humanist-reason.}
\cvitem{[194]}{\textbf{O'Donnell, Daniel Paul}. 2021d. "Upgrading a new dell XPS-13 (2021)." July 25. https://people.uleth.ca/~daniel.odonnell/blog/upgrading-a-new-dell-xps-13-2021.}
\cvitem{[193]}{\textbf{O'Donnell, Daniel Paul}. 2021c. "Gnome extensions not working in Ubuntu 21.04 (solved)." May 26. https://people.uleth.ca/~daniel.odonnell/blog/gnome-extensions-not-working-in-ubuntu-2104-solved.}
\cvitem{[192]}{\textbf{O'Donnell, Daniel Paul}. 2021b. "rescuetime doesn't record windows on Ubuntu 21.04 (solved)." May 18. https://people.uleth.ca/~daniel.odonnell/blog/rescuetime-doesn-t-record-windows-on-ubuntu-2104-solved.}
\cvitem{[191]}{\textbf{O'Donnell, Daniel Paul}. 2021a. "Setting up Firefox after new install." May 18. https://people.uleth.ca/~daniel.odonnell/blog/setting-up-firefox-after-new-install.}
\cvitem{[190]}{\textbf{O'Donnell, Daniel Paul}. 2020k. "Bulk converting and moving docx files to pdf." December 18. https://people.uleth.ca/~daniel.odonnell/blog/bulk-converting-and-moving-docx-files-to-pdf.}
\cvitem{[189]}{\textbf{O'Donnell, Daniel Paul}. 2020j. "Joining a Todoist project." November 8. https://people.uleth.ca/~daniel.odonnell/blog/joining-a-todoist-project.}
\cvitem{[188]}{\textbf{O'Donnell, Daniel Paul}. 2020i. "Crash course on translating OE verb, adjective, and noun inflections." September 17. https://people.uleth.ca/~daniel.odonnell/blog/crash-course-on-translating-oe-verb-adjective-and-noun-inflections.}
\cvitem{[187]}{\textbf{O'Donnell, Daniel Paul}. 2020h. "How to uninstall Shift from a linux computer." August 24. https://people.uleth.ca/~daniel.odonnell/blog/how-to-uninstall-shift-from-a-linux-computer.}
\cvitem{[186]}{\textbf{O'Donnell, Daniel Paul}. 2020g. "When I was a child... An interesting acknowledgement of scholarly immaturity in Ogilvie's Books known the English." July 25. https://people.uleth.ca/~daniel.odonnell/blog/when-i-was-a-child-an-interesting-acknowledgement-of-scholarly-immaturity-in-ogilvie-s-books-known-the-the-english.}
\cvitem{[185]}{\textbf{O'Donnell, Daniel Paul}. 2020f. "Using multiple signatures in Microsoft Outlook OWA (Web version)." July 6. https://people.uleth.ca/~daniel.odonnell/blog/using-multiple-signatures-in-microsoft-outlook-owa-web-version.}
\cvitem{[184]}{\textbf{O'Donnell, Daniel Paul}. 2020e. "Rotating one or more pages in a PDF in linux." March 23. https://people.uleth.ca/~daniel.odonnell/blog/rotating-one-or-more-pages-in-a-pdf-in-linux.}
\cvitem{[183]}{\textbf{O'Donnell, Daniel Paul}. 2020d. "Das Cabinet des Dr. Caligari/The Cabinet of Dr. Caligari (1920)." March 15. https://people.uleth.ca/~daniel.odonnell/blog/das-cabinet-des-dr-caligari-the-cabinet-of-dr-caligari-1920.}
\cvitem{[182]}{\textbf{O'Donnell, Daniel Paul}. 2020c. "Invention for Destruction / The Deadly Invention / The Fabulous World of Jules Verne (Vynález zkázy) 1958." February 29. https://people.uleth.ca/~daniel.odonnell/blog/invention-for-destruction-the-deadly-invention-the-fabulous-world-of-jules-verne-vynalez-zkazy-1958.}
\cvitem{[181]}{\textbf{O'Donnell, Daniel Paul}. 2020b. "If.... (1968)." February 29. https://people.uleth.ca/~daniel.odonnell/blog/if-1968.}
\cvitem{[180]}{\textbf{O'Donnell, Daniel Paul}. 2020a. "Fixing "Failure to download extra fonts" error in Ubuntu 19.10." January 19. https://people.uleth.ca/~daniel.odonnell/blog/fixing-failure-to-download-extra-fonts-error-in-ubuntu-1910.}
\cvitem{[179]}{\textbf{O'Donnell, Daniel Paul}. 2019j. "Fixing a Thunderbolt dock/display issue on Dell XPS 1300 in Ubuntu by unlocking Thunderbird." September 2. https://people.uleth.ca/~daniel.odonnell/blog/fixing-a-thunderbolt-dock-display-issue-on-dell-xps-1300-in-ubuntu-by-unlocking-thunderbird.}
\cvitem{[178]}{\textbf{O'Donnell, Daniel Paul}. 2019i. "Accessing the Oynx Boox built-in note templates." July 21. https://people.uleth.ca/~daniel.odonnell/blog/accessing-the-oynx-boox-built-in-note-templates.}
\cvitem{[177]}{\textbf{O'Donnell, Daniel Paul}. 2019h. "Jumpin' Flash Jack: Fixing a jumpy touchpad on the Dell XPS 13 9370 (Ubuntu OEM) under 19.04." July 1. https://people.uleth.ca/~daniel.odonnell/blog/jumpin-flash-jack-fixing-a-jumpy-touchpad-on-the-dell-xps-13-9370-ubuntu-oem-under-1904.}
\cvitem{[176]}{\textbf{O'Donnell, Daniel Paul}. 2019g. ""Have you checked it's plugged in?" Fixing the touchpad after an Ubuntu update (by turning it on)." June 30. https://people.uleth.ca/~daniel.odonnell/blog/have-you-checked-it-s-plugged-in-fixing-the-touchpad-after-an-ubuntu-update-by-turning-it-on.}
\cvitem{[175]}{\textbf{O'Donnell, Daniel Paul}. 2019f. "Resetting a Dell TB16 Thunderbolt dock (Updated)." March 11. https://people.uleth.ca/~daniel.odonnell/blog/resetting-a-dell-tb16-thunderbolt-dock.}
\cvitem{[174]}{\textbf{O'Donnell, Daniel Paul}. 2019e. "Fixing sensitive mouse on Dell XPS 13 9370 "Developer Edition" (i.e. Ubuntu 18.04 OEM)." March 9. https://people.uleth.ca/~daniel.odonnell/blog/fixing-sensitive-mouse-on-dell-xps-13-9370-developer-edition-ie-ubuntu-1804-oem.}
\cvitem{[173]}{\textbf{O'Donnell, Daniel Paul}. 2019d. "How to accept an invitation to a SSHRC application (Partnership Grant 2019)." February 9. https://people.uleth.ca/~daniel.odonnell/blog/how-to-accept-an-invitation-to-a-sshrc-application-partnership-grant-2019.}
\cvitem{[172]}{\textbf{O'Donnell, Daniel Paul}. 2019c. "How to accept an invitation to a SSHRC application (Organisation, Partnership Grant 2020)." February 9. https://people.uleth.ca/~daniel.odonnell/blog/how-to-accept-an-invitation-to-a-sshrc-application-organisation-partnership-grant-2020-471.}
\cvitem{[171]}{\textbf{O'Donnell, Daniel Paul}. 2019b. "How to accept an invitation to a SSHRC application (Individual, Partnership Grant 2020)." February 9. https://people.uleth.ca/~daniel.odonnell/blog/how-to-accept-an-invitation-to-a-sshrc-application-individual-partnership-grant-2020.}
\cvitem{[170]}{\textbf{O'Donnell, Daniel Paul}. 2019a. "Recovery key for Dell XPS 13 OEM Ubuntu (Developer edition)." February 8. https://people.uleth.ca/~daniel.odonnell/blog/recovery-key-for-dell-xps-13-oem-ubuntu-developer-edition.}
\cvitem{[169]}{\textbf{O'Donnell, Daniel Paul}. 2018e. "Conway's Law and Open Science: Why it feels like something's fundamentally not right." October 29. https://people.uleth.ca/~daniel.odonnell/blog/conway-s-law-and-open-science-why-it-feels-like-something-s-fundamentally-not-right.}
\cvitem{[168]}{\textbf{O'Donnell, Daniel Paul}. 2018d. "Finding files modified within a specific time period." April 21. https://people.uleth.ca/~daniel.odonnell/blog/finding-files-modified-within-a-specific-time-period.}
\cvitem{[167]}{\textbf{O'Donnell, Daniel Paul}. 2018c. "Using Zenodo as a personal repository." March 30. https://people.uleth.ca/~daniel.odonnell/blog/using-zenodo-as-a-personal-repository.}
\cvitem{[166]}{\textbf{O'Donnell, Daniel Paul}. 2018b. "Round up of citations of the Lethbridge Journal Incubator." March 30. https://people.uleth.ca/~daniel.odonnell/blog/round-up-of-citations-of-the-lethbridge-journal-incubator.}
\cvitem{[165]}{\textbf{O'Donnell, Daniel Paul}. 2018a. "Finding and replacing text in multiple files from BASH." March 28. https://people.uleth.ca/~daniel.odonnell/blog/finding-and-replacing-text-in-multiple-files-from-bash.}
\cvitem{[164]}{\textbf{O'Donnell, Daniel Paul}. 2017m. "Finding and moving off screen applications in Gnome 3/Ubuntu 17.10." December 10. https://people.uleth.ca/~daniel.odonnell/blog/finding-and-moving-off-screen-applications-in-gnome-3-ubuntu-1710.}
\cvitem{[163]}{\textbf{O'Donnell, Daniel Paul}. 2017l. "Talkin' 'bout my g- g- greatest generation? The Long November (Nablo, 1946)." December 9. https://people.uleth.ca/~daniel.odonnell/blog/talkin-bout-my-g-g-greatest-generation-the-long-november-nablo-1946.}
\cvitem{[162]}{\textbf{O'Donnell, Daniel Paul}. 2017k. "An interesting issue with the *nix ls command, or, why you should never begin a filename with a hyphen." December 5. https://people.uleth.ca/~daniel.odonnell/blog/an-interesting-issue-with-the-nix-ls-command-or-why-you-should-never-begin-a-filename-with-a-hyphen.}
\cvitem{[161]}{\textbf{O'Donnell, Daniel Paul}. 2017j. "How to fix tables that run off the page in Google Docs." November 19. https://people.uleth.ca/~daniel.odonnell/blog/how-to-fix-tables-that-run-off-the-page-in-google-docs.}
\cvitem{[160]}{\textbf{O'Donnell, Daniel Paul}. 2017i. "Master slides in Libreoffice reminders." July 10. https://people.uleth.ca/~daniel.odonnell/blog/master-slides-in-libreoffice-reminders.}
\cvitem{[159]}{\textbf{O'Donnell, Daniel Paul}. 2017h. "Linux/Chrome on Chromebook using Crouton." June 4. https://people.uleth.ca/~daniel.odonnell/blog/linux-chrome-on-chromebook-using-crouton.}
\cvitem{[158]}{\textbf{O'Donnell, Daniel Paul}. 2017g. "How to open the container folder for a Google Doc." May 14. https://people.uleth.ca/~daniel.odonnell/blog/how-to-open-the-container-folder-for-a-google-doc.}
\cvitem{[157]}{\textbf{O'Donnell, Daniel Paul}. 2017f. "Installing Vidyo on Ubuntu 16.10." May 12. https://people.uleth.ca/~daniel.odonnell/blog/installing-vidyo-on-ubuntu-1610.}
\cvitem{[156]}{\textbf{O'Donnell, Daniel Paul}. 2017e. "Displaylink and Ubuntu 16.10 and 17.04." May 11. https://people.uleth.ca/~daniel.odonnell/blog/displaylink-and-ubuntu-1610-and-1704.}
\cvitem{[155]}{\textbf{O'Donnell, Daniel Paul}. 2017d. "Date-time missing from menu bar (Ubuntu 16.10)." May 11. https://people.uleth.ca/~daniel.odonnell/blog/date-time-missing-from-menu-bar-ubuntu-1610.}
\cvitem{[154]}{\textbf{O'Donnell, Daniel Paul}. 2017c. "Updating Textpattern and Solving a Rewrite Problem." March 29. https://people.uleth.ca/~daniel.odonnell/blog/updating-textpattern-and-solving-a-rewrite-problem.}
\cvitem{[153]}{\textbf{O'Donnell, Daniel Paul}. 2017b. "The Real Crisis and the U of L... and why the Board must Act." February 15. https://people.uleth.ca/~daniel.odonnell/blog/the-real-crisis-and-the-u-of-l-and-why-the-board-must-act.}
\cvitem{[152]}{\textbf{O'Donnell, Daniel Paul}. 2017a. "Galbraith on why Universities should be contentious places." February 15. https://people.uleth.ca/~daniel.odonnell/blog/galbraith-on-why-universities-should-be-contentious-places.}
\cvitem{[151]}{\textbf{O'Donnell, Daniel Paul}. 2016z. "Some tips on getting answers to email." December 12. https://people.uleth.ca/~daniel.odonnell/blog/some-tips-on-getting-answers-to-email.}
\cvitem{[150]}{\textbf{O'Donnell, Daniel Paul}. 2016y. "How to accept an invitation to a SSHRC application." November 15. https://people.uleth.ca/~daniel.odonnell/blog/how-to-accept-an-invitation-to-a-sshrc-application.}
\cvitem{[149]}{\textbf{O'Donnell, Daniel Paul}. 2016x. "Soup to nuts: A recent piece of my writing that technology allows you to follow from idea to completion." October 27. https://people.uleth.ca/~daniel.odonnell/blog/soup-to-nuts-a-recent-piece-of-my-writing-that-technology-allows-you-to-follow-from-idea-to-completion.}
\cvitem{[148]}{\textbf{O'Donnell, Daniel Paul}. 2016w. "The bird in hand: Humanities research in the age of open data (Digital Science Report)." October 24. https://people.uleth.ca/~daniel.odonnell/blog/the-bird-in-hand-humanities-research-in-the-age-of-open-data-digital-science-report.}
\cvitem{[147]}{\textbf{O'Donnell, Daniel Paul}. 2016v. "Customized pronouns: A good idea that makes no sense (Globe and Mail)." October 24. https://people.uleth.ca/~daniel.odonnell/blog/customized-pronouns-a-good-idea-that-makes-no-sense-globe-and-mail.}
\cvitem{[146]}{\textbf{O'Donnell, Daniel Paul}. 2016u. "“Nudge nudge, say no more”: What I think needs to happen next in the Scholarly Commons Project." October 2. https://people.uleth.ca/~daniel.odonnell/blog/nudge-nudge-say-no-more-what-i-think-needs-to-happen-next-in-the-scholarly-commons-project.}
\cvitem{[145]}{\textbf{O'Donnell, Daniel Paul}. 2016t. "But does it work in theory II." September 3. https://people.uleth.ca/~daniel.odonnell/blog/but-does-it-work-in-theory-ii.}
\cvitem{[144]}{\textbf{O'Donnell, Daniel Paul}. 2016s. "But does it work in theory? Developing a generative theory for the scholarly commons." September 2. https://people.uleth.ca/~daniel.odonnell/blog/but-does-it-work-in-theory-developing-a-generative-theory-for-the-scholarly-commons.}
\cvitem{[143]}{\textbf{O'Donnell, Daniel Paul}. 2016r. "Auschwitz I and II (Birkenau): Some thoughts on a tour." July 23. https://people.uleth.ca/~daniel.odonnell/blog/auschwitz-i-and-ii-birkenau-some-thoughts-on-a-tour.}
\cvitem{[142]}{\textbf{O'Donnell, Daniel Paul}. 2016q. "Using normalize-space to fix Oxygen "pretty print" spacing problems." June 30. https://people.uleth.ca/~daniel.odonnell/blog/using-normalize-space-to-fix-oxygen-pretty-print-spacing-problems.}
\cvitem{[141]}{\textbf{O'Donnell, Daniel Paul}. 2016p. "Sweetcaptcha Wordpress Plugin deliberately creates popups." June 26. https://people.uleth.ca/~daniel.odonnell/blog/sweetcaptcha-wordpress-plugin-deliberately-creates-popups.}
\cvitem{[140]}{\textbf{O'Donnell, Daniel Paul}. 2016o. "The uleth ezproxy server." June 24. https://people.uleth.ca/~daniel.odonnell/blog/the-uleth-ezproxy-server.}
\cvitem{[139]}{\textbf{O'Donnell, Daniel Paul}. 2016n. "The CASRAI CRediT Typology." June 24. https://people.uleth.ca/~daniel.odonnell/blog/the-casrai-credit-typology.}
\cvitem{[138]}{\textbf{O'Donnell, Daniel Paul}. 2016m. "Adding annotation functions to my blog via hypothes.is." June 24. https://people.uleth.ca/~daniel.odonnell/blog/adding-annotation-functions-to-my-blog-via-hypothesis.}
\cvitem{[137]}{\textbf{O'Donnell, Daniel Paul}. 2016l. "OWA workflow." June 15. https://people.uleth.ca/~daniel.odonnell/blog/owa-workflow.}
\cvitem{[136]}{\textbf{O'Donnell, Daniel Paul}. 2016k. "Using find and rsync to extract files from a directory and move them." June 4. https://people.uleth.ca/~daniel.odonnell/blog/using-find-and-rsync-to-extract-files-from-a-directory-and-move-them.}
\cvitem{[135]}{\textbf{O'Donnell, Daniel Paul}. 2016j. "More on KISS and Tell Grading." June 3. https://people.uleth.ca/~daniel.odonnell/blog/more-on-kiss-and-tell-grading.}
\cvitem{[134]}{\textbf{O'Donnell, Daniel Paul}. 2016i. "Uleth identity/branding information and locations." May 29. https://people.uleth.ca/~daniel.odonnell/blog/uleth-identity-branding-information-and-locations.}
\cvitem{[133]}{\textbf{O'Donnell, Daniel Paul}. 2016h. "Cædmon Citation Network - Week 2." May 27. https://people.uleth.ca/~daniel.odonnell/blog/caedmon-citation-network-week-2.}
\cvitem{[132]}{\textbf{O'Donnell, Daniel Paul}. 2016g. "OWA Ninja Notes." May 18. https://people.uleth.ca/~daniel.odonnell/blog/owa-ninja-notes.}
\cvitem{[131]}{\textbf{O'Donnell, Daniel Paul}. 2016f. "How to backup an Ubuntu system using Dropbox." May 11. https://people.uleth.ca/~daniel.odonnell/blog/how-to-backup-an-ubuntu-system-using-dropbox.}
\cvitem{[130]}{\textbf{O'Donnell, Daniel Paul}. 2016e. "How to export Garageband files so that they work in other Digital Audio Workstations." February 21. https://people.uleth.ca/~daniel.odonnell/blog/how-to-export-garageband-files-so-that-they-work-in-other-digital-audio-workstations.}
\cvitem{[129]}{\textbf{O'Donnell, Daniel Paul}. 2016d. "Using hypothes.is to annotate print books." February 17. https://people.uleth.ca/~daniel.odonnell/blog/using-hypothesis-to-annotate-print-books.}
\cvitem{[128]}{\textbf{O'Donnell, Daniel Paul}. 2016c. "How to retard science? Set up a grant programme. From Leo Szilard's Mark Gable Foundation (1961)." February 17. https://people.uleth.ca/~daniel.odonnell/blog/how-to-retard-science-set-up-a-grant-programme-from-leo-szilard-s-mark-gable-foundation-1961.}
\cvitem{[127]}{\textbf{O'Donnell, Daniel Paul}. 2016b. "Harpers on the wonders of the telegraph and typewriter... and the rightful place of philologists." January 29. https://people.uleth.ca/~daniel.odonnell/blog/harpers-on-the-wonders-of-the-telegraph-and-typewriter-and-the-rightful-place-of-philologists.}
\cvitem{[126]}{\textbf{O'Donnell, Daniel Paul}. 2016a. "Advanced search functions for Google Inbox." January 5. https://people.uleth.ca/~daniel.odonnell/blog/advanced-search-functions-for-google-inbox.}
\cvitem{[125]}{\textbf{O'Donnell, Daniel Paul}. 2015q. "World is a better place 3. Career 0." December 1. https://people.uleth.ca/~daniel.odonnell/blog/world-is-a-better-place-3-career-0.}
\cvitem{[124]}{\textbf{O'Donnell, Daniel Paul}. 2015p. "Well that’s that. Solving (?) the VC model and workflow." November 30. https://people.uleth.ca/~daniel.odonnell/blog/well-that-s-that-solving-the-vc-model-and-workflow.}
\cvitem{[123]}{\textbf{O'Donnell, Daniel Paul}. 2015o. "Pitch and time stretching in Ardour." November 28. https://people.uleth.ca/~daniel.odonnell/blog/pitch-and-time-stretching-in-ardour.}
\cvitem{[122]}{\textbf{O'Donnell, Daniel Paul}. 2015n. "Mediawiki updates break previous install (solved)." November 1. https://people.uleth.ca/~daniel.odonnell/blog/mediawiki-updates-break-previous-install-solved.}
\cvitem{[121]}{\textbf{O'Donnell, Daniel Paul}. 2015m. "Using WAV samples in ARDOUR." October 17. https://people.uleth.ca/~daniel.odonnell/blog/using-wav-samples-in-ardour.}
\cvitem{[120]}{\textbf{O'Donnell, Daniel Paul}. 2015l. "Getting MIDI to work in Ardour/Jack." September 6. https://people.uleth.ca/~daniel.odonnell/blog/getting-midi-to-work-in-ardour-jack.}
\cvitem{[119]}{\textbf{O'Donnell, Daniel Paul}. 2015k. "Fixing QJackCtl." August 16. https://people.uleth.ca/~daniel.odonnell/blog/fixing-qjackctl.}
\cvitem{[118]}{\textbf{O'Donnell, Daniel Paul}. 2015j. "Dual booting Windows 10 and Ubuntu 15.04." August 8. https://people.uleth.ca/~daniel.odonnell/blog/dual-booting-windows-10-and-ubuntu-1504.}
\cvitem{[117]}{\textbf{O'Donnell, Daniel Paul}. 2015i. "Eating your cake and having it to: Solving the comment troll problem." May 27. https://people.uleth.ca/~daniel.odonnell/blog/eating-your-cake-and-having-it-to-solving-the-comment-troll-problem.}
\cvitem{[116]}{\textbf{O'Donnell, Daniel Paul}. 2015h. "First thing we do, let's kill all the authors. On subverting an outmoded tradition (Force2015 talk)." February 28. https://people.uleth.ca/~daniel.odonnell/blog/first-thing-we-do-let-s-kill-all-the-authors-on-subverting-an-outmoded-tradition-force2015-talk.}
\cvitem{[115]}{\textbf{O'Donnell, Daniel Paul}. 2015g. "Prayer as a management tool." February 27. https://people.uleth.ca/~daniel.odonnell/blog/prayer-as-a-management-tool.}
\cvitem{[114]}{\textbf{O'Donnell, Daniel Paul}. 2015f. "A "Thought Piece" on Digital Space as Simulation and the Loss of the Original." February 10. https://people.uleth.ca/~daniel.odonnell/blog/a-thought-piece-on-digital-space-as-simulation-and-the-loss-of-the-original.}
\cvitem{[113]}{\textbf{O'Donnell, Daniel Paul}. 2015e. "Faculty members' webpresence at the University of Lethbridge." February 5. https://people.uleth.ca/~daniel.odonnell/blog/faculty-members-webpresence-at-the-university-of-lethbridge.}
\cvitem{[112]}{\textbf{O'Donnell, Daniel Paul}. 2015d. "The People’s Field: The Ethos of a Humanities-Centred Social Network." February 4. https://people.uleth.ca/~daniel.odonnell/blog/the-people-s-field-the-ethos-of-a-humanities-centred-social-network.}
\cvitem{[111]}{\textbf{O'Donnell, Daniel Paul}. 2015c. "A First Law of Humanities Computing?." January 24. https://people.uleth.ca/~daniel.odonnell/blog/the-first-law-of-humanities-computing.}
\cvitem{[110]}{\textbf{O'Donnell, Daniel Paul}. 2015b. "Future Commons." January 12. https://people.uleth.ca/~daniel.odonnell/blog/future-commons.}
\cvitem{[109]}{\textbf{O'Donnell, Daniel Paul}. 2015a. "Problems with Cisco Anyconnect on Ubuntu 14.04 (Breaks Internet Connections)." January 10. https://people.uleth.ca/~daniel.odonnell/blog/problems-with-cisco-anyconnect-on-ubuntu-1404-breaks-internet-connections.}
\cvitem{[108]}{\textbf{O'Donnell, Daniel Paul}. 2014t. "Poster sessions: A great way of establishing a scholarly ecosystem in the classroom." December 26. https://people.uleth.ca/~daniel.odonnell/blog/poster-sessions-a-great-way-of-establishing-a-scholarly-ecosystem-in-the-classroom.}
\cvitem{[107]}{\textbf{O'Donnell, Daniel Paul}. 2014s. "KISS and tell grading." December 26. https://people.uleth.ca/~daniel.odonnell/blog/kiss-and-tell-grading.}
\cvitem{[106]}{\textbf{O'Donnell, Daniel Paul}. 2014r. "Code for table of contents in text pattern." November 1. https://people.uleth.ca/~daniel.odonnell/blog/code-for-table-of-contents-in-text-pattern.}
\cvitem{[105]}{\textbf{O'Donnell, Daniel Paul}. 2014q. "Testing the GRAND-DH Website." October 29. https://people.uleth.ca/~daniel.odonnell/blog/testing-the-grand-dh-website.}
\cvitem{[104]}{\textbf{O'Donnell, Daniel Paul}. 2014p. "More on Aauthors and Aalphabetical placement." July 26. https://people.uleth.ca/~daniel.odonnell/blog/more-on-aauthors-and-aalphabetical-placement.}
\cvitem{[103]}{\textbf{O'Donnell, Daniel Paul}. 2014o. "A is for Aardvark and author. The economic implications of having a last name with an early letter in the alphabet." July 26. https://people.uleth.ca/~daniel.odonnell/blog/a-is-for-aardvark-and-author-the-economic-implications-of-having-a-last-name-with-an-early-letter-in-the-alphabet.}
\cvitem{[102]}{\textbf{O'Donnell, Daniel Paul}. 2014n. "The credit line." July 13. https://people.uleth.ca/~daniel.odonnell/blog/firs-thing-we-do-let-s-kill-all-the-authors.}
\cvitem{[101]}{\textbf{O'Donnell, Daniel Paul}. 2014m. "Dangerous bug in Moodle." April 19. https://people.uleth.ca/~daniel.odonnell/blog/dangerous-bug-in-moodle.}
\cvitem{[100]}{\textbf{O'Donnell, Daniel Paul}. 2014l. "Academic Suicide." March 12. https://people.uleth.ca/~daniel.odonnell/blog/academic-suicide.}
\cvitem{[99]}{\textbf{O'Donnell, Daniel Paul}. 2014k. "Mounting University of Lethbridge "P," "R," and "W" drives under Linux." February 18. https://people.uleth.ca/~daniel.odonnell/blog/mounting-university-of-lethbridge-p-and-w-drives-under-linux.}
\cvitem{[98]}{\textbf{O'Donnell, Daniel Paul}. 2014j. "How to do a table of contents in text pattern." February 18. https://people.uleth.ca/~daniel.odonnell/blog/how-to-do-a-table-of-contents-in-text-pattern.}
\cvitem{[97]}{\textbf{O'Donnell, Daniel Paul}. 2014i. "Revisiting Old Irish: The sounds." February 11. https://people.uleth.ca/~daniel.odonnell/blog/revisiting-old-irish-the-sounds.}
\cvitem{[96]}{\textbf{O'Donnell, Daniel Paul}. 2014h. "Revisiting Old Irish: A new blog series." February 11. https://people.uleth.ca/~daniel.odonnell/blog/revisiting-old-irish-a-new-blog-series.}
\cvitem{[95]}{\textbf{O'Donnell, Daniel Paul}. 2014g. "Class 2.0: Digital technology \& digital rhetorics  in the undergraduate classroom." February 7. https://people.uleth.ca/~daniel.odonnell/blog/class-20-digital-technology-digital-rhetorics-in-the-undergraduate-classroom.}
\cvitem{[94]}{\textbf{O'Donnell, Daniel Paul}. 2014f. "Grammar and identity: Prestige, gender, and sexual orientation." February 1. https://people.uleth.ca/~daniel.odonnell/blog/grammar-and-identity-prestige-gender-and-sexual-orientation.}
\cvitem{[93]}{\textbf{O'Donnell, Daniel Paul}. 2014e. "Why doesn't anybody ever tell you this stuff? On the origins of the masculine and feminine pronouns." January 31. https://people.uleth.ca/~daniel.odonnell/blog/why-doesn-t-anybody-ever-tell-you-this-stuff-on-the-origins-of-the-masculine-and-feminine-pronouns.}
\cvitem{[92]}{\textbf{O'Donnell, Daniel Paul}. 2014d. "The problem with undoification." January 28. https://people.uleth.ca/~daniel.odonnell/blog/the-problem-with-undoification.}
\cvitem{[91]}{\textbf{O'Donnell, Daniel Paul}. 2014c. "Morphology and destiny: On words for snow and Sapir-Whorf." January 27. https://people.uleth.ca/~daniel.odonnell/blog/morphology-and-destiny-on-words-for-snow-and-sapir-whorf.}
\cvitem{[90]}{\textbf{O'Donnell, Daniel Paul}. 2014b. "Teaching prescriptive grammar hurts student writing." January 21. https://people.uleth.ca/~daniel.odonnell/blog/teaching-prescriptive-grammar-hurts-student-writing.}
\cvitem{[89]}{\textbf{O'Donnell, Daniel Paul}. 2014a. "Dolphin Language." January 21. https://people.uleth.ca/~daniel.odonnell/blog/dolphin-language.}
\cvitem{[88]}{\textbf{O'Donnell, Daniel Paul}. 2013ab. "Bibliophilia: Why books don't mean what they used to." December 24. https://people.uleth.ca/~daniel.odonnell/blog/bibliophilia.}
\cvitem{[87]}{\textbf{O'Donnell, Daniel Paul}. 2013aa. "Schuman is right that we need to get rid of the "College Paper." But wrong when she blames her students for not being able to write them. The "College Paper" has always been an exercise in futility." December 18. https://people.uleth.ca/~daniel.odonnell/blog/schuman-is-right-that-we-need-to-get-rid-of-the-college-paper.}
\cvitem{[86]}{\textbf{O'Donnell, Daniel Paul}. 2013z. "Using blogs in class." December 14. https://people.uleth.ca/~daniel.odonnell/blog/using-blogs-in-class.}
\cvitem{[85]}{\textbf{O'Donnell, Daniel Paul}. 2013y. "Yet another example of why APC Open Access should be a non-starter." October 4. https://people.uleth.ca/~daniel.odonnell/blog/yet-another-example-of-why-apc-open-access-should-be-a-non-starter.}
\cvitem{[84]}{\textbf{O'Donnell, Daniel Paul}. 2013x. ""First thing we do..." Editorial edition." September 27. https://people.uleth.ca/~daniel.odonnell/blog/first-thing-we-do-editorial-edition.}
\cvitem{[83]}{\textbf{O'Donnell, Daniel Paul}. 2013w. "Il vaut le voyage: Borges, Jane Austen, Gus van Sant, and the Zombies, or, Truth is stranger than fiction." September 22. https://people.uleth.ca/~daniel.odonnell/blog/il-vaut-le-voyage-borges-jane-austen-gus-van-sant-and-the-zombies-or-truth-is-stranger-than-fiction.}
\cvitem{[82]}{\textbf{O'Donnell, Daniel Paul}. 2013v. "Well Done, Dan and Michael." September 13. https://people.uleth.ca/~daniel.odonnell/blog/well-done-dan-and-michael.}
\cvitem{[81]}{\textbf{O'Donnell, Daniel Paul}. 2013u. "Timeline of the History of the Five-Paragraph Essay." August 17. https://people.uleth.ca/~daniel.odonnell/blog/timeline-of-the-history-of-the-five-paragraph-essay.}
\cvitem{[80]}{\textbf{O'Donnell, Daniel Paul}. 2013t. "The Ideas Create Themselves." July 25. https://people.uleth.ca/~daniel.odonnell/blog/the-ideas-create-themselves.}
\cvitem{[79]}{\textbf{O'Donnell, Daniel Paul}. 2013s. "The History of the Form Revisited." July 6. https://people.uleth.ca/~daniel.odonnell/blog/the-history-of-the-form-revisited.}
\cvitem{[78]}{\textbf{O'Donnell, Daniel Paul}. 2013r. "The Importance of Student Motivation." July 5. https://people.uleth.ca/~daniel.odonnell/blog/the-importance-of-student-motivation.}
\cvitem{[77]}{\textbf{O'Donnell, Daniel Paul}. 2013q. "Scaffolding and The Zone of Proximal Development." June 29. https://people.uleth.ca/~daniel.odonnell/blog/scaffolding-and-the-zone-of-proximal-development.}
\cvitem{[76]}{\textbf{O'Donnell, Daniel Paul}. 2013p. "Hack cross references in Workflowy." June 27. https://people.uleth.ca/~daniel.odonnell/blog/hack-cross-references-in-workflowy.}
\cvitem{[75]}{\textbf{O'Donnell, Daniel Paul}. 2013o. "Unfortunately, Planning and Structure do not Equate to Comprehension and Creativity." June 19. https://people.uleth.ca/~daniel.odonnell/blog/unfortunately-planning-and-structure-do-not-equate-to-comprehension-and-creativity.}
\cvitem{[74]}{\textbf{O'Donnell, Daniel Paul}. 2013n. "A Review of “A Machine Learning Approach For Identification of Thesis and Conclusion Statements in Student Essays"." June 6. https://people.uleth.ca/~daniel.odonnell/blog/a-review-of-a-machine-learning-approach-for-identification-of-thesis-and-conclusion-statements-in-student-essays.}
\cvitem{[73]}{\textbf{O'Donnell, Daniel Paul}. 2013m. "From Reading to Writing: Why the Essay isn’t Working." June 1. https://people.uleth.ca/~daniel.odonnell/blog/from-reading-to-writing-why-the-essay-isn-t-working.}
\cvitem{[72]}{\textbf{O'Donnell, Daniel Paul}. 2013l. "What Makes Writing Good?." May 25. https://people.uleth.ca/~daniel.odonnell/blog/what-makes-writing-good.}
\cvitem{[71]}{\textbf{O'Donnell, Daniel Paul}. 2013k. "Unessay and Standardized Testing." May 24. https://people.uleth.ca/~daniel.odonnell/blog/unessay-and-standardized-testing.}
\cvitem{[70]}{\textbf{O'Donnell, Daniel Paul}. 2013j. "Teaching Grammar." May 23. https://people.uleth.ca/~daniel.odonnell/blog/teaching-grammar.}
\cvitem{[69]}{\textbf{O'Donnell, Daniel Paul}. 2013i. "The Unessay and Metacognition." May 16. https://people.uleth.ca/~daniel.odonnell/blog/the-unessay-and-metacognition.}
\cvitem{[68]}{\textbf{O'Donnell, Daniel Paul}. 2013h. "Introduction to Unessay Research." May 15. https://people.uleth.ca/~daniel.odonnell/blog/introduction-to-unessay-research.}
\cvitem{[67]}{\textbf{O'Donnell, Daniel Paul}. 2013g. "Professor teach thyself." May 12. https://people.uleth.ca/~daniel.odonnell/blog/professor-teach-thyself.}
\cvitem{[66]}{\textbf{O'Donnell, Daniel Paul}. 2013f. "More Research Money Needed For Social Science \& Humanities." May 12. https://people.uleth.ca/~daniel.odonnell/blog/more-research-money-needed-for-social-science-humanities.}
\cvitem{[65]}{\textbf{O'Donnell, Daniel Paul}. 2013e. "Humanities, not science, key to new web frontier." May 12. https://people.uleth.ca/~daniel.odonnell/blog/humanities-not-science-key-to-new-web-frontier.}
\cvitem{[64]}{\textbf{O'Donnell, Daniel Paul}. 2013d. "Embedding Workflowy and/or Hackpad in a Wordpress site." May 9. https://people.uleth.ca/~daniel.odonnell/blog/embedding-workflowy-and-or-hackpad-in-a-wordpress-site.}
\cvitem{[63]}{\textbf{O'Donnell, Daniel Paul}. 2013c. "The meteor has struck. The dust is in the air. Let's leave the dinosaurs to their fate and concentrate on the mammals: Notes on the New Humanities." April 5. https://people.uleth.ca/~daniel.odonnell/blog/the-meteor-has-struck-the-dust-is-in-the-air-let-s-leave-the-dinosaurs-to-their-fate-and-concentrate-on-the-mammals-notes-on-the-new-humanities.}
\cvitem{[62]}{\textbf{O'Donnell, Daniel Paul}. 2013b. "The true north strong and hegemonic: Or, why do Canadians seem to run DH." March 6. https://people.uleth.ca/~daniel.odonnell/blog/the-true-north-strong-and-hegemonic-or-why-do-canadians-seem-to-run-dh.}
\cvitem{[61]}{\textbf{O'Donnell, Daniel Paul}. 2013a. "What the University of Lethbridge's short list of candidates for Dean of Arts and Science says about it as an institution." February 26. https://people.uleth.ca/~daniel.odonnell/blog/what-the-university-of-lethbridge-s-short-list-of-candidates-for-dean-of-arts-and-science-says-about-it-as-an-institution.}
\cvitem{[60]}{\textbf{O'Donnell, Daniel Paul}. 2012k. "…Done dirt cheap? Impact vs. funding in the Humanities and Social Sciences at the University of Lethbridge." October 26. https://people.uleth.ca/~daniel.odonnell/blog/done-dirt-cheap-impact-vs-funding-in-the-humanities-and-social-sciences-at-the-university-of-lethbridge.}
\cvitem{[59]}{\textbf{O'Donnell, Daniel Paul}. 2012j. "Recovering encrypted drives." September 23. https://people.uleth.ca/~daniel.odonnell/blog/recovering-encrypted-drives.}
\cvitem{[58]}{\textbf{O'Donnell, Daniel Paul}. 2012i. "How to add a twitter feed to Moodle." September 12. https://people.uleth.ca/~daniel.odonnell/blog/how-to-add-a-twitter-feed-to-moodle.}
\cvitem{[57]}{\textbf{O'Donnell, Daniel Paul}. 2012h. "MySQL cheatsheet." August 27. https://people.uleth.ca/~daniel.odonnell/blog/mysql-cheatsheet.}
\cvitem{[56]}{\textbf{O'Donnell, Daniel Paul}. 2012g. "When everyone’s super… On gaming the system." May 23. https://people.uleth.ca/~daniel.odonnell/blog/when-everyone-s-super-on-gaming-the-system.}
\cvitem{[55]}{\textbf{O'Donnell, Daniel Paul}. 2012f. "Yii Basic Steps." April 6. https://people.uleth.ca/~daniel.odonnell/blog/yii-basic-steps.}
\cvitem{[54]}{\textbf{O'Donnell, Daniel Paul}. 2012e. "Yii Ensuring that key terms are always linked." February 23. https://people.uleth.ca/~daniel.odonnell/blog/yii-ensuring-that-key-terms-are-always-linked.}
\cvitem{[53]}{\textbf{O'Donnell, Daniel Paul}. 2012d. "Understanding Relation Models in Yii." February 23. https://people.uleth.ca/~daniel.odonnell/blog/understanding-relation-models-in-yii.}
\cvitem{[52]}{\textbf{O'Donnell, Daniel Paul}. 2012c. "Creating compound attributes in Yii." February 23. https://people.uleth.ca/~daniel.odonnell/blog/creating-compound-attributes-in-yii.}
\cvitem{[51]}{\textbf{O'Donnell, Daniel Paul}. 2012b. "Adding an attribute for title to a yii widget." February 23. https://people.uleth.ca/~daniel.odonnell/blog/adding-an-attribute-for-title-to-a-yii-widget.}
\cvitem{[50]}{\textbf{O'Donnell, Daniel Paul}. 2012a. "Yii Authentication." February 18. https://people.uleth.ca/~daniel.odonnell/blog/yii-authentication.}
\cvitem{[49]}{\textbf{O'Donnell, Daniel Paul}. 2011k. "set date and time from commandzone." November 21. https://people.uleth.ca/~daniel.odonnell/blog/set-date-and-time-from-commandzone.}
\cvitem{[48]}{\textbf{O'Donnell, Daniel Paul}. 2011j. "Change date using touch." October 18. https://people.uleth.ca/~daniel.odonnell/blog/change-date-using-touch.}
\cvitem{[47]}{\textbf{O'Donnell, Daniel Paul}. 2011i. "Extracting a catalogue of element names from a collection of XML documents using XSLT 2.0." September 15. https://people.uleth.ca/~daniel.odonnell/blog/extracting-a-catalogue-of-element-names-from-a-collection-of-xml-documents-using-xslt-20.}
\cvitem{[46]}{\textbf{O'Donnell, Daniel Paul}. 2011h. "Internet on Vodaphone.nl for Samsung I896 Galaxy (Rogers, Android)." August 2. https://people.uleth.ca/~daniel.odonnell/blog/internet-on-vodaphonenl-for-samsung-i896-galaxy-rogers-android.}
\cvitem{[45]}{\textbf{O'Donnell, Daniel Paul}. 2011g. "Fixing Touchpad in Aspire One." July 18. https://people.uleth.ca/~daniel.odonnell/blog/fixing-touchpad-in-aspire-one.}
\cvitem{[44]}{\textbf{O'Donnell, Daniel Paul}. 2011f. "Recovering Attachments Opened via Microsoft Outlook." June 9. https://people.uleth.ca/~daniel.odonnell/blog/recovering-attachments-opened-via-microsoft-outlook.}
\cvitem{[43]}{\textbf{O'Donnell, Daniel Paul}. 2011e. "Pimping the Samsung Galaxy S I-896 (Rogers): Gaining Root Access, Updating Android, Unlocking, and Fixing the GPS." March 28. https://people.uleth.ca/~daniel.odonnell/blog/pimping-the-samsung-galaxy-s-i-896-rogers-gaining-root-access-updating-android-unlocking.}
\cvitem{[42]}{\textbf{O'Donnell, Daniel Paul}. 2011d. "Rooting and updating a Samsung Galaxy S I-896 (Rogers)." March 25. https://people.uleth.ca/~daniel.odonnell/blog/rooting-and-updating-a-samsung-galaxy-s-i-896-rogers.}
\cvitem{[41]}{\textbf{O'Donnell, Daniel Paul}. 2011c. "Manual Grading of All Questions in Moodle 2.0." March 20. https://people.uleth.ca/~daniel.odonnell/blog/manual-grading-of-all-questions-in-moodle-20.}
\cvitem{[40]}{\textbf{O'Donnell, Daniel Paul}. 2011b. "How to do stuff in Moodle." March 15. https://people.uleth.ca/~daniel.odonnell/blog/how-to-do-stuff-in-moodle.}
\cvitem{[39]}{\textbf{O'Donnell, Daniel Paul}. 2011a. "Modify grub menu in grub2." February 11. https://people.uleth.ca/~daniel.odonnell/blog/modify-grub-menu-in-grub2.}
\cvitem{[38]}{\textbf{O'Donnell, Daniel Paul}. 2010g. "Setting pulse to localhost before launching program." December 17. https://people.uleth.ca/~daniel.odonnell/blog/setting-pulse-to-localhost-before-launching-program.}
\cvitem{[37]}{\textbf{O'Donnell, Daniel Paul}. 2010f. "Ubuntu 10.10 Meerkat on an Acer One 521 (AO521)." December 12. https://people.uleth.ca/~daniel.odonnell/blog/ubuntu-1010-meerkat-on-an-acer-one-521-ao521.}
\cvitem{[36]}{\textbf{O'Donnell, Daniel Paul}. 2010e. "Developing complex arguments." November 15. https://people.uleth.ca/~daniel.odonnell/blog/developing-complex-arguments.}
\cvitem{[35]}{\textbf{O'Donnell, Daniel Paul}. 2010d. "Developing Essay Topics in Class." October 7. https://people.uleth.ca/~daniel.odonnell/blog/developing-essay-topics-in-class.}
\cvitem{[34]}{\textbf{O'Donnell, Daniel Paul}. 2010c. "Active Pedagogy and University English." August 17. https://people.uleth.ca/~daniel.odonnell/blog/active-pedagogy-and-university-english.}
\cvitem{[33]}{\textbf{O'Donnell, Daniel Paul}. 2010b. "DAW Notes." August 14. https://people.uleth.ca/~daniel.odonnell/blog/daw-notes.}
\cvitem{[32]}{\textbf{O'Donnell, Daniel Paul}. 2010a. "Modifying and switching between desktop interfaces in Lucid (10.4)." May 1. https://people.uleth.ca/~daniel.odonnell/blog/modifying-and-switching-between-desktop-interfaces-in-lucid-104.}
\cvitem{[31]}{\textbf{O'Donnell, Daniel Paul}. 2009h. "MYSQL Searches for use with Zencart." October 22. https://people.uleth.ca/~daniel.odonnell/blog/mysql-searches-for-use-with-zencart.}
\cvitem{[30]}{\textbf{O'Donnell, Daniel Paul}. 2009g. "Converting File Types and Media." May 25. https://people.uleth.ca/~daniel.odonnell/blog/converting-file-types-and-media.}
\cvitem{[29]}{\textbf{O'Donnell, Daniel Paul}. 2009f. "Restoring/Replacing the Bios on an Acer Aspire One." April 25. https://people.uleth.ca/~daniel.odonnell/blog/restoringreplacing-the-bios-on-an-acer-aspire-one.}
\cvitem{[28]}{\textbf{O'Donnell, Daniel Paul}. 2009e. "Installing Ubuntu 9.04 (Jaunty) on Aspire One." April 24. https://people.uleth.ca/~daniel.odonnell/blog/installing-ubuntu-904-jaunty-on-aspire-one.}
\cvitem{[27]}{\textbf{O'Donnell, Daniel Paul}. 2009d. "Music." March 1. https://people.uleth.ca/~daniel.odonnell/blog/Music.}
\cvitem{[26]}{\textbf{O'Donnell, Daniel Paul}. 2009c. "Schools of Schools of "Humanities Computing"." February 13. https://people.uleth.ca/~daniel.odonnell/blog/schools-of-schools-of-humanities-computing.}
\cvitem{[25]}{\textbf{O'Donnell, Daniel Paul}. 2009b. "MediaWiki tweaks." February 13. https://people.uleth.ca/~daniel.odonnell/blog/mediawiki-tweaks.}
\cvitem{[24]}{\textbf{O'Donnell, Daniel Paul}. 2009a. "Importing Email from Evolution to Thunderbird." February 2. https://people.uleth.ca/~daniel.odonnell/blog/importing-email-from-evolution-to-thunderbird.}
\cvitem{[23]}{\textbf{O'Donnell, Daniel Paul}. 2008p. "Byte me: Technological Education and the Humanities." December 19. https://people.uleth.ca/~daniel.odonnell/blog/byte-me-technological-education-and-the-humanities.}
\cvitem{[22]}{\textbf{O'Donnell, Daniel Paul}. 2008o. "Digital Plagiarism." December 14. https://people.uleth.ca/~daniel.odonnell/blog/digital-plagiarism.}
\cvitem{[21]}{\textbf{O'Donnell, Daniel Paul}. 2008n. "Sample badges." December 7. https://people.uleth.ca/~daniel.odonnell/blog/sample-badges.}
\cvitem{[20]}{\textbf{O'Donnell, Daniel Paul}. 2008m. "Within the Hollow Crown: A Sad Tale of the Death of Kings (Radio Play)." November 25. https://people.uleth.ca/~daniel.odonnell/blog/within-the-hollow-crown-a-sad-tale-of-the-death-of-kings-radio-play.}
\cvitem{[19]}{\textbf{O'Donnell, Daniel Paul}. 2008l. "Installing Ubuntu (8.10 Intrepid Ibex) on Acer Aspire One Netbook." November 15. https://people.uleth.ca/~daniel.odonnell/blog/installing-ubuntu-810-intrepid-ibex-on-acer-aspire-one-netbook.}
\cvitem{[18]}{\textbf{O'Donnell, Daniel Paul}. 2008k. "Installing RefDB Bibliographic Server." October 12. https://people.uleth.ca/~daniel.odonnell/blog/installing-refdb-bibliographic-server.}
\cvitem{[17]}{\textbf{O'Donnell, Daniel Paul}. 2008j. "Handy Linux Commands." October 12. https://people.uleth.ca/~daniel.odonnell/blog/handy-linux-commands.}
\cvitem{[16]}{\textbf{O'Donnell, Daniel Paul}. 2008i. "Using the M-Audio Audiophile USB Digital Audio Interface with Linux." September 7. https://people.uleth.ca/~daniel.odonnell/blog/using-the-m-audio-audiophile-usb-digital-audio-interface-with-linux.}
\cvitem{[15]}{\textbf{O'Donnell, Daniel Paul}. 2008h. "How to save PDF forms without buying proprietary software such as Adobe Acrobat." September 5. https://people.uleth.ca/~daniel.odonnell/blog/how-to-save-pdf-forms-without-buying-proprietary-software-such-as-adobe-acrobat.}
\cvitem{[14]}{\textbf{O'Donnell, Daniel Paul}. 2008g. "Using Oxygen and Subversion client." August 20. https://people.uleth.ca/~daniel.odonnell/blog/using-oxygen-and-subversion-client.}
\cvitem{[13]}{\textbf{O'Donnell, Daniel Paul}. 2008f. "Setting up Evolution as a Microsoft Exchange Client at the U of L." August 19. https://people.uleth.ca/~daniel.odonnell/blog/setting-up-evolution-as-a-microsoft-exchange-client-at-the-u-of-l.}
\cvitem{[12]}{\textbf{O'Donnell, Daniel Paul}. 2008e. "Lost in Logout Land: Running Scripts on Login and Logout (Partially Solved but Interesting Anyway)." July 16. https://people.uleth.ca/~daniel.odonnell/blog/lost-in-logout-land-running-scripts-on-login-and-logout-partially-solved-but-interesting-anyway.}
\cvitem{[11]}{\textbf{O'Donnell, Daniel Paul}. 2008d. "Enable root access to Ubuntu via ssh." May 14. https://people.uleth.ca/~daniel.odonnell/blog/enable-root-access-to-ubuntu-via-ssh.}
\cvitem{[10]}{\textbf{O'Donnell, Daniel Paul}. 2008c. "Unlocking the Samsung YP-K3J for use with as a USB Mass Storage Device with OGG Vorbis Support." May 4. https://people.uleth.ca/~daniel.odonnell/blog/unlocking-the-samsung-yp-k3j-for-use-with-as-a-usb-mass-storage-device-with-ogg-vorbis-support.}
\cvitem{[9]}{\textbf{O'Donnell, Daniel Paul}. 2008b. "Overriding Screen Resolution on Xorg in Ubuntu." April 27. https://people.uleth.ca/~daniel.odonnell/blog/overriding-screen-resolution-on-xorg-in-ubuntu.}
\cvitem{[8]}{\textbf{O'Donnell, Daniel Paul}. 2008a. "Fixing wireless start in Ubuntu Gutsy (NOT SOLVED)." March 30. https://people.uleth.ca/~daniel.odonnell/blog/fixing-wireless-start-in-ubuntu-gutsy.}
\cvitem{[7]}{\textbf{O'Donnell, Daniel Paul}. 2007c. "Academic Freedom, or What's with the bananas?." December 3. https://people.uleth.ca/~daniel.odonnell/blog/academic-freedom-or-whats-with-the-bananas.}
\cvitem{[6]}{\textbf{O'Donnell, Daniel Paul}. 2007b. "Two things I'm glad Linux has improved." May 17. https://people.uleth.ca/~daniel.odonnell/blog/two-things-im-glad-linux-has-improved.}
\cvitem{[5]}{\textbf{O'Donnell, Daniel Paul}. 2007a. "Object oriented PHP5: In the land of the blind." April 2. https://people.uleth.ca/~daniel.odonnell/blog/object-oriented-php5-in-the-land-of-the-blind.}
\cvitem{[4]}{\textbf{O'Donnell, Daniel Paul}. 2006d. "Custom Keyboard in Linux/X11." December 8. https://people.uleth.ca/~daniel.odonnell/blog/custom-keyboard-in-linuxx11.}
\cvitem{[3]}{\textbf{O'Donnell, Daniel Paul}. 2006c. "Two things I wish Linux distributions could improve." November 18. https://people.uleth.ca/~daniel.odonnell/blog/two-things-i-wish-linux-distributions-could-improve.}
\cvitem{[2]}{\textbf{O'Donnell, Daniel Paul}. 2006b. "Textpattern." November 18. https://people.uleth.ca/~daniel.odonnell/blog/textpattern.}
\cvitem{[1]}{\textbf{O'Donnell, Daniel Paul}. 2006a. "Using SSH to Access Multiple Machines at a Single Domain." November 17. https://people.uleth.ca/~daniel.odonnell/blog/using-ssh-to-access-multiple-machines-at-a-single-domain.}
